---
title: "analysis"
author: "Devynn M Wulstein"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

```{r}
## Loading libraries
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
```


```{r}
# Loading dataframe(s)
AllDataFrame <- load("data/Patch_And_Colony_Data_20201103.rdata")
```

```{r}
# Defining site IDs, genera names, and transition intervals (years) as lists
SiteNames <- as.character(unique(ColonyLevel$Site))
GeneraNames <- as.character(unique(ColonyLevel$Genus_Code))
IntervalYears <- unique(ColonyLevel$Interval_Years)
```

The aim of this analysis is to calculate the kernel fits (growth, survival, & reproduction) for each combination of genera-site-year and then each separately. 

Full models:
(1) Each Genera for all sites & interval years
(2) Each Site for all genera & interval years
(3) Each Interval Year for all sites & genera

Individual models: (the more realistic models that we are more interested in)
(1) Each Genera by interval year, sites are not separated
(2) Each Genera by site, interval years are not separated
(3) Each genera by site and interval year (we will have parameter values that equal site * interval years * genera)

```{r FULLmodGROWTH, eval = TRUE}
# initializing the data runs for the growth analysis

# define the parms for model loop
Focus <- GeneraNames #change this each run
LoopLength <- length(Focus)
Spec_selection <- ColonyLevel$Genus_Code #change this each run

# defining the matrix which holds the slope/int for each model run in the loop
growth <- matrix(0, nrow = 2, ncol = LoopLength)


for (i in 1:LoopLength){
  # subsetting to specifiy which interactions (genera/site/year) we care about
  subset1 <- subset(ColonyLevel, Spec_selection == Focus[i])
  
  # subsetting for growth & shrinkage
  subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                   TransitionTypeSimple == "SHRINK")
  
  # running the linear regression model
  modG <- lm(ln_ES ~ ln_SS ,data = subset2)
  
  # saving the model
  growth[,i] <- coef(modG)
  
}

# moving model coefs into a list
# need to define the column names
Glist <- list(g.int = growth[1,], g.slp = growth[2,])

# for each model grouping: 
# Comment out before new run
 Glist_genera <- Glist # Full model 1
# Glist_site <- Glist # Full model 2
# Glist_years <- Glist # Full model 3
 
```

```{r Plotting full growth models, }
plot(ln_ES ~ ln_SS ,data = ColonyLevel)
abline(a=Glist_genera$g.int[1], b=Glist_genera$g.slp[1], col='red', lwd=2)
abline(a=Glist_genera$g.int[2], b=Glist_genera$g.slp[2], col='blue', lwd=2)
abline(a=Glist_genera$g.int[3], b=Glist_genera$g.slp[3], col='green', lwd=2)
legend("topleft", bty = "n", lty = c(1,1), col = c("red","blue","green"),
       legend= GeneraNames , cex = 0.8)

#plot each genus separately
#use par(mfrow)


```




Each Genera by interval year, sites are not separated
Growth (line 116) is messed up
```{r IndividualGrowthMods, eval=TRUE}
# initializing the data runs for the growth analysis

# define the parms for model loop
Focus <- GeneraNames
subFocus <- IntervalYears
LoopLength <- length(Focus)
LoopLengthSF <- length(subFocus)
Spec_selection <- ColonyLevel$Genus_Code
Spec_selectionSF <- ColonyLevel$Interval_Years
# defining the matrix which holds the slope/int for each model run in the loop
growth <- matrix(0, nrow = 2, ncol = (LoopLength * LoopLengthSF))


for (i in 1:LoopLength){
  # subsetting to specifiy which interactions (genera/site/year) we care about
  subset1 <- subset(ColonyLevel, Spec_selection == Focus[i])
  for (v in 1:LoopLengthSF) {
    subset2 <- subset(subset1, Spec_selectionSF == subFocus[v])
    # subsetting for growth & shrinkage
    subset3 <- subset(subset2, TransitionTypeSimple == "GROWTH" | 
                   TransitionTypeSimple == "SHRINK")
  
  # running the linear regression model
    modG <- lm(ln_ES ~ ln_SS ,data = subset3)
  
  # saving the model
    growth[,i] <- coef(modG)
  }
}

# moving model coefs into a list
# need to define the column names
Glist <- list(g.int = growth[1,], g.slp = growth[2,])

# for each model grouping: 
# Comment out before new run
# Glist_genera <- Glist # Full model 1
# Glist_site <- Glist # Full model 2
# Glist_years <- Glist # Full model 3

```

#TO DO
Fix growth line
Then run individual models 2 & 3
Plot each genus separately (full model)
Plot each full model
Plot each individual model
Figure out how to save into dataframe
Repeat for survival
Repeat for reproduction


