---
title: "analysis"
author: "Devynn M Wulstein"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

```{r}
## Loading libraries
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
```


```{r}
# Loading dataframe(s)
AllDataFrame <- load("data/Patch_And_Colony_Data_20201103.rdata")
```

```{r}
# Defining site IDs, genera names, and transition intervals (years) as lists
SiteNames <- as.character(unique(ColonyLevel$Site))
GeneraNames <- as.character(unique(ColonyLevel$Genus_Code))
IntervalYears <- unique(ColonyLevel$Interval_Years)
```

The aim of this analysis is to calculate the kernel fits (growth, survival, & reproduction) for each combination of genera-site-year and then each separately. 

Full models:
(1) Each Genera for all sites & years
(2) Each Site for all genera & years
(3) Each Year for all sites & genera

Individual models: (the more realistic models that we are more interested in)
(1) Each Genera by year, sites are not seperated
(2) Each Genera by site, years are not seperated
(3) Each genera by site and year (we will have parameter values that equal site * years * genera)

```{r GROWTH,}
# initializing the 
```