---
title: "VitalRateFunctions"
author: "Caroline Rodriguez"
date: "1/25/2021"
output: html_document
---

#Libraries
```{r}
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
```

#Set up
```{r}
setwd("/Users/c-rod/Documents/R_data/VitalRates/")
#load in .rdata file
load(file = "/Users/c-rod/Documents/R_data/VitalRates/Patch_And_Colony_Data_20201103.rdata")

View(ColonyLevel)
#View(PatchLevel)


```

#Subset by Site
Going to use ColonyLevel data to avoid all the fission/fusion confusion
```{r}
MAISIOK01 <- subset(ColonyLevel, Site=="MAI_SIO_K01")
#View(MAISIOK01)
KUROCC010 <- subset(ColonyLevel, Site=="KUR_OCC_010")
#View(KUROCC010)
PHROCC016 <- subset(ColonyLevel, Site=="PHR_OCC_016")
#View(PHROCC016)
HAWOCC002 <- subset(ColonyLevel, Site=="HAW_OCC_002")
HAWOCC003 <- subset(ColonyLevel, Site=="HAW_OCC_003")
HAWOCC010 <- subset(ColonyLevel, Site=="HAW_OCC_010")
HAWSIOK08 <- subset(ColonyLevel, Site=="HAW_SIO_K08")
HAWSIOK10 <- subset(ColonyLevel, Site=="HAW_SIO_K10")
MAIOCC002 <- subset(ColonyLevel, Site=="MAI_OCC_002")
OAH022 <- subset(ColonyLevel, Site=="OAH_XXX_022")
OAHOCC010 <- subset(ColonyLevel, Site=="OAH_OCC_010")

```

#Combined Growth Function
```{r}
#should we restrict data to colonies > 20cm2?

#plot starting size and ending size for growth. Get a best fit line for that data
growth <- subset(ColonyLevel, TransitionTypeSimple == "GROWTH")
#growth[!is.na(growth$TransitionRate_L)]
View(growth)

#plo <- ggplot(growth, aes(x=ln_SS, y=TransitionRate_L, shape=TransitionTypeSimple)) + 
  #geom_point(size=1) +
    #ylim(1,5)
#plo
#his <- hist(growth$StartingSize, breaks = 1000, xlim = c(0,50) )



#For growth function, will fit using starting vs ending size, log transformed because to exaggerate small differences (b/c I have so many little pieces and lots of instances of little growth)
growth_plot = ggplot(data = growth, aes(x=ln_SS, y=ln_ES,color=TransitionTypeSimple,shape=TransitionTypeSimple)) + 
  geom_point() + geom_abline(slope = 1)+
  ggtitle("Growth: All Genera and All Species") +
  #scale_x_sqrt(breaks=c(10,50,100,250,500,1000,2000),limits=c(0,400))+ #log transform x axis
  #scale_y_sqrt(breaks=c(10,50,100,250,500,1000,2000),limits=c(0,400))+
  scale_shape_manual(values=0:4)+
  theme_bw()+ #facet_grid separates by Genus Code (makes 3 verticle plots) and Site (makes horizontal plots)
  xlab("Colony Size at Time T (cm^2)") + ylab("Colony Size at Time T+1 (cm^2)")
growth_plot


fit_allgrowth <- lm(ln_ES ~ ln_SS ,data = growth)
fit_allgrowth
summary(fit_allgrowth)
#linear model for growth function
#y = 0.8480942x + 1.0746995
plot(ln_ES ~ ln_SS ,data = growth, xlim=c(-3,10), ylim=c(-3,10), main = "Growth: All Genera and All Species", xlab = "Log Starting Size", ylab = "Log Ending Size", legend(x=9, y=4) )
abline(fit_allgrowth)
abline(a=0, b=1,col="red")
#smaller sizes grow faster and the larger sizes are right at the 1:1


```

#Growth function: separate by Genus
```{r}
#plot based on Genus
growth_plot_genus = ggplot(data = growth, aes(x=ln_SS, y=ln_ES,color=TransitionTypeSimple,shape=TransitionTypeSimple)) + 
  geom_point() + geom_abline(slope = 1)+
  #scale_x_sqrt(breaks=c(10,50,100,250,500,1000,2000),limits=c(0,400))+ #log transform x axis
  #scale_y_sqrt(breaks=c(10,50,100,250,500,1000,2000),limits=c(0,400))+
  scale_shape_manual(values=0:4)+
  facet_grid(c("Genus_Code"))+theme_bw()+ #facet_grid separates by Genus Code (makes 3 verticle plots) and Site (makes horizontal plots)
  xlab("Colony Size at Time T (cm^2)") + ylab("Colony Size at Time T+1 (cm^2)")
growth_plot_genus


#Pocillopora
growth_POCS <- subset(growth, Genus_Code == "POCS")
#View(growth_POCS)

#function
fit_POCS <- lm(ln_ES ~ ln_SS ,data = growth_POCS)
fit_POCS
summary(fit_POCS)
#linear model for growth function
#y = 0.6516999x + 2.2245910
plot(ln_ES ~ ln_SS ,data = growth_POCS ,xlim=c(-3,10), ylim=c(-3,10), main="All Pocillopora growth at all sites" )  
abline(fit_POCS)
abline(a=0, b=1,col="red")
#everyone's growing and smaller sizes grow supa faster and the larger sizes are right at the 1:1


####################
#Porites
growth_POSP <- subset(growth, Genus_Code == "POSP")
#View(growth_POSP)

#function
fit_POSP <- lm(ln_ES ~ ln_SS ,data = growth_POSP)
fit_POSP
#linear model for growth function
#y = 0.8462x + 1.0236
summary(fit_POSP)
plot(ln_ES ~ ln_SS ,data = growth_POSP ,xlim=c(-3,10), ylim=c(-3,10), main="All Porites growth at all sites")
abline(fit_POSP)
abline(a=0, b=1,col="red")
#smaller sizes grow faster and the larger sizes are right at the 1:1


####################
#Montipora
growth_MOSP <- subset(growth, Genus_Code == "MOSP")
#View(growth_MOSP)

#function
fit_MOSP <- lm(ln_ES ~ ln_SS ,data = growth_MOSP)
fit_MOSP
#linear model for growth function
#y = 0.8559x + 0.9507
summary(fit_MOSP)
#legend isn't working
plot(ln_ES ~ ln_SS ,data = growth_MOSP ,xlim=c(-3,10), ylim=c(-3,10), main="All Montipora growth at all sites")
#legend("topleft", legend = c("Line1","Line2"))
abline(fit_MOSP)
abline(a=0, b=1,col="red")

#another way to plot all montipora
ggplot(growth_MOSP, aes(x=ln_SS, y=ln_ES))+ geom_point() + geom_smooth(method = lm)+
  ggtitle("All Montipora growth at all sites")+
  annotate("rect", xmin =-.5, xmax = .5, ymin = 4.5, ymax = 5.5, fill="white", colour="red") +
  annotate("text", x=0, y=5, label = "R^2=0.93") 
#smaller sizes grow faster and the larger sizes are right at the 1:1

```

#Growth function: separate by site, all genera
```{r}
#MAISIOK01
growth_MAISIOK01 <- subset(MAISIOK01, TransitionTypeSimple == "GROWTH")
#function
fit_MAISIOK01 <- lm(ln_ES ~ ln_SS ,data = growth_MAISIOK01)
fit_MAISIOK01
#linear model for growth function:  y = 0.8826x + 0.7377
#plot
summary(fit_MAISIOK01)
plot(ln_ES ~ ln_SS ,data = growth_MAISIOK01 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at MAISIOK01")
abline(fit_MAISIOK01)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_MAISIOK01)
#interpret results
anova(fit_MAISIOK01)

###################
#KUROCC010
growth_KUROCC010 <- subset(KUROCC010, TransitionTypeSimple == "GROWTH")
#function
fit_KUROCC010 <- lm(ln_ES ~ ln_SS ,data = growth_KUROCC010)
fit_KUROCC010
#linear model for growth function:  y = 0.8024x + 1.6121
#plot
summary(fit_KUROCC010)
plot(ln_ES ~ ln_SS ,data = growth_KUROCC010 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at KUROCC010") 
abline(fit_KUROCC010)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_KUROCC010)
#interpret results
anova(fit_KUROCC010)


###################
#PHROCC016
growth_PHROCC016 <- subset(PHROCC016, TransitionTypeSimple == "GROWTH")
#function
fit_PHROCC016 <- lm(ln_ES ~ ln_SS ,data = growth_PHROCC016)
fit_PHROCC016
#linear model for growth function:  y = 0.7812x + 1.4363
#plot
summary(fit_PHROCC016)
plot(ln_ES ~ ln_SS ,data = growth_PHROCC016 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at PHROCC016") 
abline(fit_PHROCC016)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_PHROCC016)
#interpret results
anova(fit_PHROCC016)

###################
#HAWOCC002 
growth_HAWOCC002 <- subset(HAWOCC002, TransitionTypeSimple == "GROWTH")
#function
fit_HAWOCC002 <- lm(ln_ES ~ ln_SS ,data = growth_HAWOCC002)
fit_HAWOCC002
#linear model for growth function:  y = 0.7677x + 1.0998
#plot
summary(fit_HAWOCC002)
plot(ln_ES ~ ln_SS ,data = growth_HAWOCC002 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at HAWOCC002") 
abline(fit_HAWOCC002)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_HAWOCC002)
#interpret results
anova(fit_HAWOCC002)

###################
#HAWOCC003
growth_HAWOCC003 <- subset(HAWOCC003, TransitionTypeSimple == "GROWTH")
#function
fit_HAWOCC003 <- lm(ln_ES ~ ln_SS ,data = growth_HAWOCC003)
fit_HAWOCC003
#linear model for growth function:  y = 0.8936x + 0.8542
#plot
summary(fit_HAWOCC003)
plot(ln_ES ~ ln_SS ,data = growth_HAWOCC003 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at HAWOCC003") 
abline(fit_HAWOCC003)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_HAWOCC003)
#interpret results
anova(fit_HAWOCC003)

###################
#HAWOCC010
growth_HAWOCC010 <- subset(HAWOCC010, TransitionTypeSimple == "GROWTH")
#function
fit_HAWOCC010 <- lm(ln_ES ~ ln_SS ,data = growth_HAWOCC010)
fit_HAWOCC010
#linear model for growth function:  y = 0.8041x + 1.1056
#plot
summary(fit_HAWOCC010)
plot(ln_ES ~ ln_SS ,data = growth_HAWOCC010 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at HAWOCC010") 
abline(fit_HAWOCC010)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_HAWOCC010)
#interpret results
anova(fit_HAWOCC010)

###################
#HAWSIOK08
growth_HAWSIOK08 <- subset(HAWSIOK08, TransitionTypeSimple == "GROWTH")
#function
fit_HAWSIOK08 <- lm(ln_ES ~ ln_SS ,data = growth_HAWSIOK08)
fit_HAWSIOK08
#linear model for growth function:  y = 0.8201x + 1.3385
#plot
summary(fit_HAWSIOK08)
plot(ln_ES ~ ln_SS ,data = growth_HAWSIOK08 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at HAWSIOK08") 
abline(fit_HAWSIOK08)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_HAWSIOK08)
#interpret results
anova(fit_HAWSIOK08)

###################
#HAWSIOK10
growth_HAWSIOK10 <- subset(HAWSIOK10, TransitionTypeSimple == "GROWTH")
#function
fit_HAWSIOK10 <- lm(ln_ES ~ ln_SS ,data = growth_HAWSIOK10)
fit_HAWSIOK10
#linear model for growth function:  y = 0.7471x + 1.6589
#plot
summary(fit_HAWSIOK10)
plot(ln_ES ~ ln_SS ,data = growth_HAWSIOK08 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at HAWSIOK10") 
abline(fit_HAWSIOK10)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_HAWSIOK10)
#interpret results
anova(fit_HAWSIOK10)

###################
#MAIOCC002
growth_MAIOCC002 <- subset(MAIOCC002, TransitionTypeSimple == "GROWTH")
#function
fit_MAIOCC002 <- lm(ln_ES ~ ln_SS ,data = growth_MAIOCC002)
fit_MAIOCC002
#linear model for growth function:  y = 0.813x + 1.422
#plot
summary(fit_MAIOCC002)
plot(ln_ES ~ ln_SS ,data = growth_MAIOCC002 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at MAIOCC002") 
abline(fit_MAIOCC002)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_MAIOCC002)
#interpret results
anova(fit_MAIOCC002)

###################
#OAH022
growth_OAH022 <- subset(OAH022, TransitionTypeSimple == "GROWTH")
#function
fit_OAH022 <- lm(ln_ES ~ ln_SS ,data = growth_OAH022)
fit_OAH022
#linear model for growth function:  y = 0.7992x + 1.4419
#plot
summary(fit_OAH022)
plot(ln_ES ~ ln_SS ,data = growth_OAH022 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at OAH022") 
abline(fit_OAH022)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_OAH022)
#interpret results
anova(fit_OAH022)

###################
#OAHOCC010
growth_OAHOCC010 <- subset(OAHOCC010, TransitionTypeSimple == "GROWTH")
#function
fit_OAHOCC010 <- lm(ln_ES ~ ln_SS ,data = growth_OAHOCC010)
fit_OAHOCC010
#linear model for growth function:  y = 0.9324x + 0.6625
#plot
summary(fit_OAH022)
plot(ln_ES ~ ln_SS ,data = growth_OAH022 ,xlim=c(-3,10), ylim=c(-3,10), main="All genera growth at OAHOCC010") 
abline(fit_OAH022)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_OAH022)
#interpret results
anova(fit_OAH022)


```

#Growth by Site and Genus
one site, separate by genera
```{r}
#MAISIOK01
gro_MAISIOK01_POSP <- subset(growth_MAISIOK01, Genus_Code == "POSP")
#function
fit_MAISIOK01_POSP <- lm(ln_ES ~ ln_SS ,data = gro_MAISIOK01_POSP)
fit_MAISIOK01_POSP
#linear model for growth function:  y = 0.9182x + 0.5546
#plot
summary(fit_MAISIOK01_POSP)
plot(ln_ES ~ ln_SS ,data = gro_MAISIOK01_POSP ,xlim=c(-3,10), ylim=c(-3,10), main="Porites growth at MAISIOK01")
abline(fit_MAISIOK01_POSP)
abline(a=0, b=1,col="red")
#plot residuals
par(mfrow=c(2,2))
plot(fit_MAISIOK01_POSP)
#interpret results
anova(fit_MAISIOK01_POSP)
 

```


Compare r2 values
Do a likliehood or AIC comparison to compare model fit and determine the best one?
#AIC comparison
https://www.scribbr.com/statistics/akaike-information-criterion/
```{r}
#Going to compare genus model vs. site model vs. site+genus
fit_POCS
fit_MAISIOK01
fit_MAISIOK01_POSP

```



Mortality function
Use binomial to fit (logit function)

```{r Survival, cache=FALSE}
## Starting with suvival/mortality of all (genera + site + year)

# s.mod <- glm(surv ~ area + area_2, family="binomial", data)

# genera <- # Particular genus name we care about
# genz <- ColonyLevel[ColonyLevel$Genus_Code == genera]
# d_site <- # site name
# sitez <- ColonyLevel
# a_data_mort <- subset(ColonyLevel, TransitionTypeSimple == "MORT") 
# ps <- subset(a_data_mort, Genus_Code == "POSP")

surv <- 1 - ColonyLevel$Mortality

bad <- which(ColonyLevel$ln_SS == "-Inf")
ColonyLevel$ln_SS[bad] <- 'NA'

bad2 <- which(ColonyLevel$ln_SS == "-Inf")
ColonyLevel$ln_SS[bad2] <- 'NA'

gn <- glm(Mortality ~ ln_SS, family = "binomial", data = ColonyLevel, 
          na.action = na.pass)

inv.logit <- function(x){
  exp(x)/(1+exp(x))
}

# plot(ColonyLevel$ln_SS, surv, xlab = 'Area (ln of area)', ylab = 'Survival')
# This isn't really showing anything...
plot(jitter(surv, 0.1) ~ ln_SS, ColonyLevel)
points(ColonyLevel$ln_SS, inv.logit(predict(gn)), pch=8)


```


